---
title: "R Project"
author: "Shaun Stanley"
date: "29/10/2021"
output: html_document
---

```{r}
library(tidyverse)
library(humaniformat) # used to convert from First Name Last Name to Last Name, First Name
library(tidytext)
library(gutenbergr)
```

## Import data

```{r gutenberg_works}
temp <- gutenberg_works()
```

```{r gutenberg_kipling_download, eval=FALSE}
kipling_download <- gutenberg_works() %>%
                        filter(str_detect(author, "Kipling")) %>% 
                      gutenberg_download(mirror="https://gutenberg.pglaf.org/", meta_fields = c("title", "author"))

```

```{r gutenberg_twain_download, eval=FALSE}
twain_download <- gutenberg_works() %>%
                        filter(str_detect(author, "Twain")) %>% 
                      gutenberg_download(mirror="https://gutenberg.pglaf.org/", meta_fields = c("title", "author"))
```


## Backing up data

```{r backup_data, eval=FALSE}
write_csv(twain_download, "twain_download.csv")
```

```{r backup_data, eval=FALSE}
write_csv(kipling_download, "kipling_download.csv")
```

## Restoring data

```{r restore_data}
kipling_import <- read_csv("kipling_download.csv")
twain_import <- read_csv("twain_download.csv")
```

```{r}
kipling_import <- kipling_import %>%
    mutate(year = case_when(title == "Plain Tales from the Hills" ~ "1888",
                          title == "Soldiers Three" ~ "1888",
                          title == "The Man Who Would Be King" ~ "1888",
                          title == "The Phantom Rickshaw and Other Ghost Stories" ~ "1888",
                          title == "Under the Deodars" ~ "1888",
                          title == "Wee Willie Winkie and Other Stories Volume 2" ~ "1888",
                          title == "In Black and White" ~ "1889",
                          title == "Indian Tales" ~ "1819",
                          title == "The Light that Failed" ~ "1890",
                          title == "Life's Handicap" ~ "1891",
                          title == "The Bridge Builders" ~ "1893",
                          title == "The Jungle Book" ~ "1894",
                          title == "The Second Jungle Book" ~ "1895",
                          title == "Captains Courageous" ~ "1896",
                          title == "Soldier Stories" ~ "1896",
                          title == "Soldiers Three Part 2" ~ "1897",
                          title == "The City of Dreadful Night" ~ "1898",
                          title == "The Day's Work Volume 1" ~ "1898",
                          title == "Rewards and Fairies" ~ "1899",
                          title == "Stalky and Co" ~ "1899",
                          title == "Kim" ~ "1901",
                          title == "Just So Stories" ~ "1902",
                          title == "With the Night Mail" ~ "1909",
                          title == "The Eyes of Asia" ~ "1916",
                          title == "Land and Sea Tales for Boys and Girls" ~ "1923",)) %>% # Adds the corresponding years to each title
  arrange(year) # Arranging the table by year
```

```{r}
twain_import <- twain_import %>%
    mutate(year = case_when(title == "A Connecticut Yankee" ~ "1889",
                          title == "Those Extraordinary Twins" ~ "1893",
                          title == "The Tragedy of Pudd'nhead Wilson" ~ "1893",
                          title == "Adventures of Huckleberry Finn" ~ "1884",
                          title == "The Adventures of Tom Sawyer" ~ "1876",
                          title == "Personal Recollections of Joan of Arc" ~ "1896",
                          title == "The Stolen White Elephant" ~ "1882",
                          title == "The American Claimant" ~ "18",
                          title == "The sÌ1,000,000 bank-note, and other new stories" ~ "1893",
                          title == "Alonzo Fitz, and Other Stories" ~ "1904",
                          title == "Tom Sawyer, Detective" ~ "1896",
                          title == "The Prince and the Pauper" ~ "1881",
                          title == "The Mysterious Stranger A Romance" ~ "1916",
                          title == "The Man That Corrupted Hadleyburg, and Other Stories" ~ "1900",
                          title == "Tom Sawyer Abroad" ~ "1894",
                          title == "The $30,000 Bequest, and Other Stories" ~ "1906",
                          title == "A Tramp Abroad" ~ "1880",
                          title == "The Innocents abroad" ~ "1869",
                          title == "The Mysterious Stranger, and Other Stories" ~ "1916",
                          title == "Personal Recollections of Joan of Arc Volume 2" ~ "1896",
                          title == "A Double Barrelled Detective Story" ~ "1902",
                          title == "Roughing It" ~ "1872",
                          title == "A Horse's Tale" ~ "1906",
                          title == "Life on the Mississippi" ~ "1883",)) %>% # Adds the corresponding years to each title
  arrange(year) # Arranging the table by year
```

## Modelling Data

### Adding Author

```{r kipling_author}
kipling_authors <- bind_rows(kipling_import)
```

```{r twain_author}
twain_authors <- bind_rows(twain_import)
```

```{r kipling_column}
kipling_authors <- kipling_authors %>% 
                mutate(author ="Kipling")
```

```{r twain_column}
twain_authors <- twain_authors %>% 
                mutate(author ="Twain")
```

```{r all_authors}
all_authors <- bind_rows(kipling_authors, twain_authors)
```

### Tidying the Text

```{r tidy_all_authors}
tidy_all_authors <- all_authors %>% 
                    unnest_tokens(word, text) %>% 
                    anti_join(stop_words)
```

### Creating operationalizing words

Now that we have our corpus in place, we can do some more "feature engineering" by marking each time one of our two operational concepts occurs: bravery and duty.

We can create two separate lexicons and join them to the table.

```{r adding_words}
bravery_words <- c("brave","adventure", "confident", "confidently", "courage", "fear")

bravery_df <- data_frame(word = bravery_words, bravery = TRUE)

duty_words <- c("duty", "burden", "job", " work","ought")

duty_df <- data_frame(word = duty_words, duty = TRUE)
```

#We can add these words by using a left_join. A left join will keep everything on left hand side 

```{r tagged_words}
all_authors_tagged <- tidy_all_authors %>% 
                                left_join(bravery_df) %>% 
                                left_join(duty_df)
```

#We can then establish some basic percentages for the use of each word.

```{r calculate_words}
all_authors_table <- all_authors_tagged %>% 
                     group_by(author) %>% 
                     count(bravery, duty) %>% 
                     mutate (percent = n/sum(n)*100)
```

```{r load_libraries}
library(gutenbergr)
library(tidytext)
library(tidyverse)
library(scales)
library(ggthemes)
```

## Part 2: Basic EDA with ggplot

```{r relative_frequency_long}
all_authors_frequency <- all_authors_tagged %>%
  group_by(title) %>%
  add_count(name = "length") %>%
  mutate(bravery_count = sum(bravery, na.rm = TRUE)) %>%
  mutate(relative_frequency = bravery_count / length) %>%
  select(author, title, relative_frequency) %>% 
  distinct()
```

#This is quite a number of steps. We can refactor this with the `summarise` function to read:

```{r relative_frequency_short, message=FALSE}
all_authors_frequency_short <- all_authors_tagged %>%
  group_by(author, title) %>%
  summarise(relative_frequency_short =
              sum(bravery, na.rm = TRUE) / n())
```

### Grouping variables in a histogram`

```{r histogram_bravery_duty}
all_authors_tagged %>%
  group_by(author, title) %>%
  #Run the same summary function, but instead of only creating one column                      create two.
  summarise(
    bravery = sum(bravery, na.rm = TRUE) / n(),
    duty = sum(duty, na.rm = TRUE) / n()
  ) %>%
  #Pivot the table longer and put the column names next to their relative                      frequency values.
  pivot_longer(bravery:duty,
               names_to = "concept",
               values_to = "relative_frequency") %>%
  #Clean up the variable by capitalizing them.
  mutate(author = str_to_title(author), concept =
           str_to_title(concept)) %>%
  ggplot(aes(relative_frequency, fill = author)) +
  geom_histogram(
    color = "black",
    alpha = .5,
    position = "identity",
    bins = 5
  ) +
  labs(title = "Romance and Technology by Gender and Author",
       x = "Relative Frequency of Technology and Romance Words",
       y = "Number of Texts",
       fill = "Author") +
  facet_wrap(vars(author, concept)) +
  theme_clean()
```



